Machine Learning Methods for Site-specific Input Management

### 2022-03-18 Codes/PrepareResults.rmd

@@

```{r}
vis_RMSE_y_eonr <-
  res_y_test %>%
  .[sim %in% c(10, 20, 30) & Method %in% c("RF", "BRF", "CNN") & Model == "aabbyytt"] %>%
  ggplot() +
  geom_point(aes(x = rmse_y, y = rmse_optN, shape = Method, fill = factor(sim)), size = 2) +
  scale_shape_manual(values = c(21, 23, 25)) +
  guides(
    fill = guide_legend(override.aes = list(shape = 21))
  ) +
  labs(fill = "Simulation Round", shape = "Method") +
  # guides(fill = "none") +
  # facet_wrap( ~ Model, ncol = 2) +
  ylim(NA, 95) +
  labs(y = " RMSE of EONR Estimation (kg/ha)") +
  labs(x = " RMSE of Yield Prediction (kg/ha)") +
  theme_dist
```

@@

>>>>

```{r}
# === Low error field map === #
field_cell_low_sf <- 
  here("Shared/Results/for_writing/sample_field_cell_low_sf.rds") %>%
  readRDS()

field_m_error_low <- 
  ggplot(field_cell_low_sf) +
    geom_sf(aes(fill = yield_error), size = 0) +
    scale_fill_viridis_c() +
    labs(fill = expression(paste( ~ epsilon, " (kg/ha)"))) +
    ggtitle("(1) Low error") +
    theme_figure

# === High error field map === #
field_cell_high_sf <- 
  here("Shared/Results/for_writing/sample_field_cell_high_sf.rds") %>%
  readRDS()

field_m_error_high <- 
  ggplot(field_cell_high_sf) +
    geom_sf(aes(fill = yield_error), size = 0) +
    scale_fill_viridis_c() +
    labs(fill = expression(paste( ~ epsilon, " (kg/ha)"))) +
    ggtitle("(1) High error") +
    theme_figure
```

@@

```{r}
# sim_no <- c(300, 600, 900)
# sim_no <- c(10, 20, 30)

vis_RMSE_y_eonr <-
  res_y_test %>%
  .[sim %in% sim_no & Method %in% c("RF", "BRF", "CNN") & Model == "aabbyytt"] %>%
  ggplot() +
    geom_point(aes(x = rmse_y, y = rmse_optN, shape = Method, fill = factor(sim)), size = 2) +
    scale_shape_manual(values = c(21, 23, 25)) +
    ylim(NA, 95) +
    labs(y = " RMSE of EONR Estimation (kg/ha)") +
    labs(x = " RMSE of Yield Prediction (kg/ha)") +
    theme_dist +
    labs(fill="Simulation Round", shape="Method") +
    guides(fill = guide_legend(override.aes=list(shape=21))) +
    # guides(fill=guide_legend(nrow=2, byrow=TRUE)) +
    # guides(shape=guide_legend(nrow=2, byrow=TRUE)) +
    theme(legend.position="bottom", legend.box="vertical", legend.margin=margin()) +
    labs(fill="Simulation Round", shape="Method") 
```

@@

# Various Error Size (Appendix)

## Low error

```{r}
Simres_low <- readRDS(here("Shared/Results/for_writing/forest_summry_bySim_low.rds"))

# === Preparation === #
table_optN_prep_low <-
  Simres_low%>%
  .[, .(
    rmse_optN = format(round(mean(rmse_optN), 1), nsmall = 1),
    pi_loss = format(round(mean(pi_loss), 2), nsmall = 2)
  ), by = .(type, Method, Model)] %>%
  dcast(type + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
  .[, `:=`(
    blank1 = NA, blank2 = NA, blank3 = NA
  )] %>%
  .[, .(type, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CF_base, pi_loss_CF_base)]

# === Summary Table (Testing Data sets) === #
report_table_optN_low <-
  table_optN_prep_low %>%
  .[type == "test", !"type"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  # add_row(.after = 4) %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Model = "Model",
    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
    # blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
    blank3 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(3:4, 6:7, 9:10), part = "header") %>%
  add_header(
    Model = "",
    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
    # blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
    blank3 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
    top = FALSE
  ) %>%
  compose(i = 2, j = c(4, 7, 10), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # autofit() %>%
  # width(j = c(2,5,8,11), width=0.3) %>%
  # fix_border_issues()
  footnote(
    # i = 1, j = c(4, 7, 10, 13), part = "header",
    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(3, 4, 6, 7, 9, 10), width = 0.6) %>%
  width(j = c(2, 5, 8), width = 0.1)

#/*--------------------------------*/
#' ## Yield prediction
#/*--------------------------------*/ 
report_table_y_low <-
  Simres_low %>%
  .[type == "test" & Method %in% c("RF", "BRF")] %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit()
```

## High error

```{r}
#/*--------------------------------*/
#' ## EONR estimation
#/*--------------------------------*/
Simres_high <- readRDS(here("Shared/Results/for_writing/forest_summry_bySim_high.rds"))

# === Preparation === #
table_optN_prep_high <-
  Simres_high%>%
  .[, .(
    rmse_optN = format(round(mean(rmse_optN), 1), nsmall = 1),
    pi_loss = format(round(mean(pi_loss), 2), nsmall = 2)
  ), by = .(type, Method, Model)] %>%
  dcast(type + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
  .[, `:=`(
    blank1 = NA, blank2 = NA, blank3 = NA
  )] %>%
  .[, .(type, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CF_base, pi_loss_CF_base)]

# === Summary Table (Testing Data sets) === #
report_table_optN_high <-
  table_optN_prep_high %>%
  .[type == "test", !"type"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  # add_row(.after = 4) %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Model = "Model",
    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
    # blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
    blank3 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(3:4, 6:7, 9:10), part = "header") %>%
  add_header(
    Model = "",
    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
    # blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
    blank3 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
    top = FALSE
  ) %>%
  compose(i = 2, j = c(4, 7, 10), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # autofit() %>%
  # width(j = c(2,5,8,11), width=0.3) %>%
  # fix_border_issues()
  footnote(
    # i = 1, j = c(4, 7, 10, 13), part = "header",
    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(3, 4, 6, 7, 9, 10), width = 0.6) %>%
  width(j = c(2, 5, 8), width = 0.1)

#/*--------------------------------*/
#' ## Yield prediction
#/*--------------------------------*/ 
report_table_y_high <-
  Simres_high %>%
  .[type == "test" & Method %in% c("RF", "BRF")] %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit()
```
